---
title: "Allcott & Gentzkow （2017）"
author: "Dan Xu"
date: "3/16/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Import dataset
```{r}
# library("reticulate")
# import("pandas")
# 
# # Set the path to the Python executable file
# use_python("/opt/anaconda3/bin/python", required = T)
# 
# # config <- system2(command = python, args = paste0('"', config_script, '"'), stdout = TRUE, stderr=T)
# 
# # Check the version of Python.
# py_config()
```

```{r}
# import pandas as pd
# 
# def main():
#     measures   = ['Traffic_Sources',
#                   'Monthly_Visits']
#     categories = {'News': 50,
#                   'News_Newspapers': 21,
#                   'Society_Politics': 20,
#                   'fake': 13}
# 
#     
#         for category in categories.keys():
#         for measure in measures:
#             data = pd.DataFrame()
#             for num in range(categories[category]):
#                 new = initialize_data('source/raw/Alexa/%s/%s_%s.csv' %(category, measure, num + 1), category)
#                 data = data.append(new)
#             data.to_csv('output/data/Alexa/%s_%s.txt' %(category, measure),
#               sep = '|', header = True, index = True, index_label = 'mother')
# 
# def initialize_data(infile, category):
#     data = pd.read_csv(infile, sep = ',', skiprows = range(0, 6), header = 0)
#     data.set_index('Metric', inplace = True)
#     data.drop('Date', axis = 1, inplace = True)
#     data.index.name = None
#     data = data.transpose()
#     data['category'] = category
#     return data
# 
# main()
```

Load libraries 
```{r}
library(ggplot2)
library(tidyverse)
library(forcats)  # recoding
library(psych)  # testing for internal consistency
library(ggpubr)
theme_set(theme_pubr())
```

Save the post_stratification survey as a .rData file
```{r}
 Survey <- read.csv("/Users/dans/Documents/Github/Social_media_fake_news/Inputs/Data/113992-V1/election-media-JEP-replication/source/raw/Inputs/Data/PostElectionSurvey/Sheet_1.csv",header = TRUE, sep = ",", encoding = "UTF-16")
```

Clean the dataset
```{r}
Survey_clean <-
  Survey[, -c(1:9)]
```
glimpse at the data
```{r}
glimpse(Survey_clean) #messey, needs rename and recode 
```

Rename cols/variables
```{r}
names(Survey_clean)[1] <- "consent"
names(Survey_clean)[2] <- "Honesty"
```
How often do you get news from the following channels. 
```{r}
names(Survey_clean)[3] <- "News_socialmedia"
names(Survey_clean)[4] <- "News_web/app"


ggplot(Survey_clean, aes(News_socialmedia)) +
  geom_bar(fill = "#0073C2FF") +
  theme_pubclean() 


longer_survey_socialmedia <- 
  Survey_clean %>% 
  select(News_socialmedia,`News_web/app`) %>% 
  pivot_longer(`News_socialmedia`:`News_web/app`, names_to = "question", values_to = "response")
print(longer_survey_socialmedia)

longer_survey_socialmedia %>% 
  na.omit() %>% 
ggplot(aes(x = response,fill = question)) +
  geom_bar() +
  facet_wrap(vars(question), ncol = 3) +
  labs(x = "Response (on a 1 to 4 scale)", y = "Number of respondents")


```

Clear column names_demographic questions 
```{r}
colnames(Survey_clean)[grep("What.is.your.age.", colnames(Survey_clean))] <-"age"
colnames(Survey_clean)[grep("What.is.your.gender.", colnames(Survey_clean))] <-"gender"
colnames(Survey_clean)[grep("Which.race.ethnicity.best.describes.you", colnames(Survey_clean))] <-"ethnicity"
colnames(Survey_clean)[grep("How.much.total.combined.money.did.all.members.of.your.HOUSEHOLD.earn.last.year.", colnames(Survey_clean))] <-"income"
colnames(Survey_clean)[grep("What.is.the.highest.degree.or.level.of.school.you.have.completed.", colnames(Survey_clean))] <-"education"
colnames(Survey_clean)[grep("Device.Types", colnames(Survey_clean))] <-"device_type"
colnames(Survey_clean)[grep("In.what.ZIP.code.is.your.home.located", colnames(Survey_clean))] <-"zipcode"
```


Partisanship
```{r}
colnames(Survey_clean)[grep("Before.the.2016.election..did.you.consider.yourself.a.Republican..a.Democrat..an.Independent..or.what." , colnames(Survey_clean))] <-"partyid"
```

Plots demographic information 
```{r}

longer_survey_demographic <- 
  Survey_clean %>% 
  select(partyid, education,ethnicity,age:income) %>% 
  pivot_longer(partyid:income, names_to = "question", values_to = "response")
print(longer_survey_demographic)

longer_survey_demographic %>% 
  na.omit() %>% 
ggplot(aes(x = response,fill = question)) +
  geom_bar() +
  facet_wrap(vars(question), ncol = 3) +
  labs(x = "Response", y = "Number of respondents")

# describe(longer_survey_demographic$income)

```





Voting behavior
```{r}
colnames(Survey_clean)[grep("Who.did.you.vote.for.in.the.2016.presidential.election.", colnames(Survey_clean))] <-"vote_who"
colnames(Survey_clean)[grep("When.did.you.make.up.your.mind.about.who.to.vote.for.", colnames(Survey_clean))] <-"vote_when"
```

Social media usage
```{r}
colnames(Survey_clean)[grep("In.this.survey..we.ll.ask.you.about..social.media...by.which.we.mean.Facebook..Twitter..YouTube..Reddit..and.the.like..Do.you.ever.use.social.media."  , colnames(Survey_clean))] <-"social_media_often"

colnames(Survey_clean)[grep("Think.about.your.network.of.online..friends..and.other.people.you.follow.or.interact.with.on.social.media.", colnames(Survey_clean))] <-"social_media_preferred"

# Think about your network of online "friends" and other people you follow or
# interact with on social media.¬†What share of them do you think¬†preferred the
# same presidential candidate as you?


colnames(Survey_clean)[grep("hink.about.the.month.leading.up.to.the.2016.election..On.average..how.many.minutes.per.day.would.you.say.you.spent.reading", colnames(Survey_clean))] <-"news_mmins"

colnames(Survey_clean)[grep( "Of.those.minutes..how.many.were.spent.reading..watching..or.listening.to.election.news.on.social.media.", colnames(Survey_clean))] <-"news_mmins_social"

colnames(Survey_clean)[grep( "Which.of.those.sources.was.your..strong.most.important..strong..source.of.news.and.information.about.the.2016.election."  , colnames(Survey_clean))] <-"news_source"
```

Pope.Francis endorsement 
```{r}
colnames(Survey_clean)[grep( "X.Pope.Francis.endorsed.Donald.Trump..", colnames(Survey_clean))] <-"Francis" #Question Viewed
names(Survey_clean)[17] <- "Francis1"
levels(as.factor(Survey_clean$Francis)) #Do you recall seeing this reported or discussed¬†prior to the election?


# At the time of the election, would your best guess have been that this
# statement was true?
names(Survey_clean)[18] <- "Francis_endorsement"

```
Clinton illegal arms
```{r}
names(Survey_clean)[19] <- "Cliton_question" #Question Viewed
names(Survey_clean)[20] <- "Cliton_arms" #Do you recall seeing this reported or discussed¬†prior to the election?
levels(as.factor(Survey_clean$Cliton_question)) 
levels(as.factor(Survey_clean$Cliton_arms)) 
names(Survey_clean)[21] <- "Cliton_true" #At the time of the election, would your best guess have been that this statement was true?

```

Ireland accepts asylum under Trump presidency
```{r}
names(Survey_clean)[22] <- "Ireland_question" #Question Viewed
names(Survey_clean)[23] <- "Ireland_asylum"#Do you recall seeing this reported or discussed¬†prior to the election?
names(Survey_clean)[24] <- "Ireland_true"
```

 the FBI uncovered evidence of a pedophile sex ring
 
```{r}
names(Survey_clean)[25] <- "FBI_question" #Question Viewed
names(Survey_clean)[26] <- "FBI_Clinton"#Do you recall seeing this reported or discussed¬†prior to the election?
names(Survey_clean)[27] <- "FBI_true"
```
FBI director 
```{r}
names(Survey_clean)[28] <- "Comey_question" #Question Viewed
names(Survey_clean)[29] <- "Comey_invsetigation"#Do you recall seeing this reported or discussed¬†prior to the election?
names(Survey_clean)[30] <- "Comey_true"
```

Trump tax plan 
```{r}
names(Survey_clean)[31] <- "tax_question"
names(Survey_clean)[32] <- "tax_Trump"
names(Survey_clean)[33] <- "tax_true"
```

Clinton paied Beyonce and J.Z.
```{r}
names(Survey_clean)[34] <- "Beyonce_question"
names(Survey_clean)[35] <- "Beyonce_Clinton"
names(Survey_clean)[36] <- "Beyonce_true"
```

Trump deported Mirada
```{r}
names(Survey_clean)[37] <- "Miranda_question"
names(Survey_clean)[38] <- "Miranda_deported"
names(Survey_clean)[39] <- "Miranda_true"
```

illary.Clinton.s.first.name.was.spelled.with.an.extra..i
```{r}
names(Survey_clean)[40] <- "spelled_question"
names(Survey_clean)[41] <- "spelled_Clinton"
names(Survey_clean)[42] <- "spelled_true"
```

Clinton campaign planed a scheme by taking Republican voters to a wrong place
```{r}
names(Survey_clean)[43] <- "scheme_question"
names(Survey_clean)[44] <- "scheme_Clinton"
names(Survey_clean)[45] <- "schme_true"
```
FBI director Comey communited with Clinton about email releaase
```{r}
names(Survey_clean)[46] <- "email_question"
names(Survey_clean)[47] <- "email_Clinton"
names(Survey_clean)[48] <- "email_true"
```

Clinton deviates funds 
```{r}
names(Survey_clean)[49] <- "funds_question"
names(Survey_clean)[50] <- "funds_Clinton"
names(Survey_clean)[51] <- "funds_true"
```

Clinton said Trump supporters deplorables
```{r}
names(Survey_clean)[52] <- "deplorables_question"
names(Survey_clean)[53] <- "deplorables_Clinton"
names(Survey_clean)[54] <- "deplorables_true"
```

Donald.Trump.refused.to.say.whether.he.would.concede.the.election.if.he.lost
```{r}
names(Survey_clean)[55] <- "lost_question"
names(Survey_clean)[56] <- "lost_Trump"
names(Survey_clean)[57] <- "lost_true"
```

Beyonce.and.Jay.Z.appeared.at.a.rally.in.support.of.Hillary.Clinton
```{r}
names(Survey_clean)[58] <- "support_question"
names(Survey_clean)[59] <- "support_Clinton"
names(Survey_clean)[60] <- "support_true"
```



```{r}
# extra_colnames <- names(Survey_clean)  # save names in this vector
# 
# names(Survey_clean)[3:65] <- paste("i", formatC(1:63, width = 2, flag = "0"), sep = "") 
```



How did you vote for in 2016

```{r}

```
The plots show that 



```{r}
 saveRDS(Survey, file = "/Users/dans/Documents/Github/Social_media_fake_news/Inputs/Data/113992-V1/election-media-JEP-replication/source/raw/Inputs/Data/PostElectionSurvey/survey.rData")
```

Load the survey
```{r}
survey <- load("/Users/dans/Documents/Github/Social_media_fake_news/Inputs/Data/113992-V1/election-media-JEP-replication/source/raw/Inputs/Data/PostElectionSurvey/survey.rData")

```


# Abstract 

In the theoretical framework of the economics of fake news,Hunt Allcott and Matthew Gentzkow (2017) conducted a survey and discovered that fake news was widely shared in favor of Donald Trump.


# Intro 
Survey 

# Data 
Post election survey 
115 pro-Trump fake stories
41 pro-Clinton fake stories

# EDA 





